---
title: "DATA607_Assignment_2"
author: "PeiMing_Chen"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r}
library(tidyverse)
```

### Introduction
A database of a CSV file that established in MySQL Workbench was loaded into Rstudio. I collected six movies reviews from five of my friends. Through R, I did some rating analysis and data cleaning of this database.  

```{r}
Ratingsdata <- data.frame(read.csv("https://raw.githubusercontent.com/PMCformosa/DATA607_Assignment2/main/DATA607_WeeK_2_SQL_CSV.csv", header = TRUE))

head(Ratingsdata)
```

### Average rating of each movie from five of my friends
Null values were filtered out from Ratings 
```{r}
avgerage_Ratings <- Ratingsdata %>%
  group_by(MovieName) %>%
  filter(Ratings != "NULL") %>%
  summarise(avg= mean(as.integer(Ratings)))
avgerage_Ratings
```

From this bar plot we can easily tell that "MEGAN" has the highest rating among the six movies currently showing in theaters. 
```{r}
library(ggplot2)
ggplot(data=avgerage_Ratings, aes(x=avg, y=MovieName , fill=MovieName)) + 
  geom_bar(stat="identity")
```

Visualization of how these five friends rate these six movies is shown in the plot below. Null value of each reviewer is replaced by rating= 0 in each plot. 

```{r}
library(ggplot2)
data_01 = Ratingsdata
data_01[,4][data_01[,4] == "NULL"] <- 0
ggplot(data=data_01, aes(x=MovieName, y = Ratings, fill = MovieName, label = Ratings))+
    geom_bar(stat="identity")+ 
    facet_wrap(~FirstName)+
    ggtitle("Movie Ratings by each Friend")+
    theme(axis.text.x = element_blank(),plot.title = element_text(hjust=0.5),legend.position = "right")
```



